\documentclass[10pt,aspectratio=169]{beamer}

% Theme and Styling
\usetheme{Madrid}
\usecolortheme{whale}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[frame number]

% Packages
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes, arrows.meta, positioning}
\usepackage{booktabs}

\title[MedBlock Contributions]{MedBlock v2: Team Contributions \& Infrastructure Ownership}
\subtitle{Detailed Breakdown for Ankit, Mohit, and Ronit}
\date{\today}

\begin{document}

% Title Panel (Not counted in the 9 core slides, but standard)
\begin{frame}
    \titlepage
\end{frame}

% ---------------------------------------------------------
% SECTION 1: ANKIT
% ---------------------------------------------------------

% Slide 1: Ankit Overview
\begin{frame}{Ankit: Lead Infrastructure Architect}
    \begin{block}{Role Overview}
        Responsible for overall network orchestration, Docker Swarm management, deployment automation, and the Manager Governance portal.
    \end{block}
    \vspace{0.5cm}
    \textbf{Key Contributions:}
    \begin{itemize}
        \item \textbf{Docker Swarm Orchestration:} Clustered physical laptops into a single logical network using overlay mesh routing over Tailscale VPN.
        \item \textbf{Automation Scripts:} Developed \texttt{deploy.sh} to automate cryptographic key generation and SCP distribution across nodes.
        \item \textbf{Governance UI:} Built the Manager backend/frontend where hospital admins securely register new Doctors and generate X.509 certificates.
    \end{itemize}
\end{frame}

% Slide 2: Ankit Containers
\begin{frame}{Ankit: Container Ownership (PC1 / Swarm Master)}
    Ankit operates \textbf{PC1}, which acts as the root of the network and Swarm Master.
    \vspace{0.5cm}
    
    \textbf{Containers Hosted on PC1:}
    \begin{enumerate}
        \item \textbf{Fabric CA (Certificate Authority):} The root of cryptographic trust. Generates identities for all organizations.
        \item \textbf{Raft Orderer:} Ensures network consensus. Receives executed transactions, orders them into blocks, and broadcasts them.
        \item \textbf{Peer0 (Org1):} The anchor peer for the organization.
        \item \textbf{CouchDB0:} The state database exclusively attached to Peer0.
        \item \textbf{Manager Portal:} The React application authorizing network access.
    \end{enumerate}
\end{frame}

% Slide 3: Ankit Deep Dive
\begin{frame}{Ankit: Technical Deep Dive}
    \begin{center}
        \textbf{Solving the Genesis Problem}
    \end{center}
    \vspace{0.2cm}
    Hyperledger requires absolute cryptographic synchronization before starting.
    \begin{itemize}
        \item \textbf{The Challenge:} Worker nodes (PC2/PC3) cannot boot their peers without their explicit private keys.
        \item \textbf{The Solution:} The \texttt{deploy.sh} script dynamically intercepts the generated MSP (Membership Service Provider) keys from the CA and securely pushes them to Mohit and Ronit's disk volumes via SCP \textit{before} signaling Docker Swarm to deploy the containers over the overlay network.
    \end{itemize}
\end{frame}

% ---------------------------------------------------------
% SECTION 2: MOHIT
% ---------------------------------------------------------

% Slide 4: Mohit Overview
\begin{frame}{Mohit: Smart Contract Lead \& Clinical Frontends}
    \begin{block}{Role Overview}
        Responsible for the Fabric Chaincode (business logic), state database integration, and the privacy-focused clinical frontends (Patient/Pharmacist).
    \end{block}
    \vspace{0.5cm}
    \textbf{Key Contributions:}
    \begin{itemize}
        \item \textbf{Chaincode Architecture:} Developed Node.js Smart Contracts defining structures for \textit{PatientRecord}, \textit{Prescription}, and \textit{AccessGrant}.
        \item \textbf{Patient Self-Sovereignty:} Built the Patient UI where certificates guarantee users can exclusively view their own files.
        \item \textbf{Off-Chain Integrity:} Integrated the React UI with the IPFS network for decentralized storage of heavy medical PDFs.
    \end{itemize}
\end{frame}

% Slide 5: Mohit Containers
\begin{frame}{Mohit: Container Ownership (PC2 / Worker Node 1)}
    Mohit operates \textbf{PC2}, adding decentralization and executing smart contracts.
    \vspace{0.5cm}
    
    \textbf{Containers Hosted on PC2:}
    \begin{enumerate}
        \item \textbf{Peer1 (Org1):} Executes the transaction proposals. It hosts the Chaincode Docker container alongside it.
        \item \textbf{CouchDB1:} The state database exclusively attached to Peer1. 
        \item \textbf{Patient App Container:} The React portal for patient logins.
        \item \textbf{Pharmacist App Container:} The React portal for billing access.
    \end{enumerate}
\end{frame}

% Slide 6: Mohit Deep Dive
\begin{frame}{Mohit: Technical Deep Dive}
    \begin{center}
        \textbf{CouchDB Rich Queries \& ABAC}
    \end{center}
    \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{Why CouchDB?} Replaced default LevelDB with CouchDB. This allows the Chaincode to execute complex JSON ('Mango') queries, such as instantly fetching all unfulfilled prescriptions for a specific Hospital without scanning the entire blockchain.
        \item \textbf{ABAC (Attribute-Based Access Control):} The Pharmacist frontend proves our privacy model. The Chaincode validates the Pharmacist's certificate and strictly returns only the medicine name to the UI, explicitly hiding the Patient's private medical diagnosis.
    \end{itemize}
\end{frame}

% ---------------------------------------------------------
% SECTION 3: RONIT
% ---------------------------------------------------------

% Slide 7: Ronit Overview
\begin{frame}{Ronit: Integration Architect \& Gateway Developer}
    \begin{block}{Role Overview}
        Responsible for the API Gateway (translating web requests to Blockchain actions), Fabric SDK bridging, and the full-stack Inventory Application.
    \end{block}
    \vspace{0.5cm}
    \textbf{Key Contributions:}
    \begin{itemize}
        \item \textbf{Fabric API Gateway:} Built the central Node.js backend integrating the \texttt{fabric-network} SDK to securely sign HTTP transactions.
        \item \textbf{Wallet Management:} Managed the FileSystemWallet mapping X.509 physical identities to active routing sessions.
        \item \textbf{Supply Chain Trust:} Built the Inventory UI and integrated it with the core blockchain logic for automated stock tracking.
    \end{itemize}
\end{frame}

% Slide 8: Ronit Containers
\begin{frame}{Ronit: Container Ownership (PC3 / Worker Node 2)}
    Ronit operates \textbf{PC3}, ensuring strict High Availability and Fault Tolerance.
    \vspace{0.5cm}
    
    \textbf{Containers Hosted on PC3:}
    \begin{enumerate}
        \item \textbf{Peer2 (Org1):} Independent peer ensuring network survival if PC2 fails. Receives data via Gossip Dissemination.
        \item \textbf{CouchDB2:} Maintains a mirrored, synchronized ledger state.
        \item \textbf{Backend API Gateway Container:} The Node.js SDK server translating all REST calls to gRPC payload binaries.
        \item \textbf{Inventory App Container:} The React portal tracking medicine.
    \end{enumerate}
\end{frame}

% Slide 9: Ronit Deep Dive
\begin{frame}{Ronit: Technical Deep Dive}
    \begin{center}
        \textbf{Immutable Supply Chain Deductions}
    \end{center}
    \vspace{0.2cm}
    \begin{itemize}
        \item \textbf{The Gateway Bridge:} React Apps cannot speak the binary gRPC language required by Fabric. The API Gateway intercepts standard web payloads, loads the user's secure certificate, and executes the mathematical transaction signatures automatically.
        \item \textbf{Fraud Prevention:} Integrated the Inventory backend logic with Mohit's Pharmacist API. When a prescription is fulfilled, the API atomically triggers an \texttt{invokeChaincode} deduction. This permanently alters the ledger, making it mathematically impossible to dispense medicine without a trace.
    \end{itemize}
\end{frame}

\end{document}
