\chapter{Conclusion and Future Scope}

\section{Conclusion}

The Electronic Health Record (EHR) project successfully demonstrates a production-ready, decentralized platform built on Hyperledger Fabric v2.5 and deployed across a three-node Docker Swarm cluster. The project addresses critical shortcomings of centralized healthcare systems by providing:

\begin{enumerate}
    \item \textbf{Data Immutability:} All patient records, prescriptions, and inventory transactions are permanently recorded on the blockchain with cryptographic audit trails, eliminating the possibility of unauthorized data modification.
    
    \item \textbf{Patient Self-Sovereignty:} Through ABAC-driven access control and X.509 certificate-based authentication, patients have granular control over who accesses their medical records, including the ability to grant and revoke access to specific healthcare providers.
    
    \item \textbf{Decentralized Deployment:} The three-node Swarm architecture connected via Tailscale VPN proves that Hyperledger Fabric can operate across geographically distributed nodes with automatic ledger synchronization via the Gossip protocol.
    
    \item \textbf{Supply Chain Integrity:} The atomic linkage between the Billing Portal and Inventory Application ensures that every medicine dispensation is permanently traced on the ledger, preventing pharmaceutical fraud through ghost prescriptions.
    
    \item \textbf{Operational Automation:} The single-command \texttt{deploy.sh} script automates the entire network lifecycle, from cryptographic key generation to chaincode installation, reducing deployment complexity from hours to minutes.
\end{enumerate}

The team-based distributed development approach, with each member owning specific infrastructure components and application portals, mirrors real-world DevOps practices and demonstrates the practical feasibility of multi-stakeholder blockchain deployments in healthcare settings.

\section{Future Scope}

The following enhancements are planned for future iterations of the Electronic Health Record (EHR) system:

\begin{enumerate}
    \item \textbf{Multi-Organization Support:} Extend the network from a single organization (Org1MSP) to multiple hospital organizations, each with independent Certificate Authorities and private data collections for inter-hospital data sharing.
    
    \item \textbf{Byzantine Fault Tolerance:} Replace the Raft Ordering Service with a BFT-based consensus mechanism (such as Hyperledger Fabric's BFT Orderer in v3.0) to tolerate malicious nodes in a multi-organization deployment.
    
    \item \textbf{Private Data Collections:} Implement Fabric's Private Data Collections (PDC) to enable selective data sharing between specific organizations without exposing sensitive information to the entire channel.
    
    \item \textbf{AI-Powered Analytics:} Integrate machine learning models for predictive medicine inventory management, automated drug interaction detection, and anomaly detection in billing patterns.
    
    \item \textbf{Mobile Application:} Develop native mobile applications (Android/iOS) for patient self-service, enabling real-time access to medical records, appointment scheduling, and telemedicine integration.
    
    \item \textbf{Zero-Knowledge Proofs:} Incorporate ZKP-based verification to prove medical conditions (e.g., vaccination status) without revealing the underlying patient diagnosis, further strengthening privacy guarantees.
    
    \item \textbf{Performance Benchmarking:} Conduct comprehensive throughput and latency benchmarking using Hyperledger Caliper to establish baseline performance metrics under varying transaction loads.
\end{enumerate}
